Article Title

### 2013-08-09 sections/Simulation.tex
added Figure 2: regularization target as graphical models.
Added figure with simulation results.

\subsection{Simulation}
To illustrate,

\textbf{Figure 2.}{
Simulation results. 
\textbf{A}: A $100 \times 100$ covariance matrix without a low-dimensional structure, a sample covariance with n=2000, distributions of true and sample correlation coefficients, eigenspectra of true and sample covariances.
\textbf{B}: A similar covariance matrix with 8 factors.
\textbf{C}: A similar covariance matrix with sparse inverse. 
\textbf{D}: A similar covariance matrix with sparse + low-rank inverse with 3 latent units.
\textbf{E}: Risk convergence rates
}\label{fig:02}

>>>>

To illustrate

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure3.pdf}
\caption{
%\textbf{Figure 3.}{
Simulation results.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
}\label{fig:03}
%}
\end{figure}
